Analytical Model for the Current Density in the Electrochemical Synthesis of Porous Silicon Structures with a Lateral Gradient

### 2020-11-17 paper.tex
Shorten abstract to 150 words

\begin{document}
\shorttitle{Model of the Current Density in the Electrochemical
  Synthesis of PS Structures with a Lateral Gradient}
\shortauthors{Ospina-Delacruz et al.}
\title[mode=title]{Analytical Model for the Current Density in
the Electrochemical Synthesis of Porous Silicon Structures with a
Lateral Gradient}
\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0002-9609-3031]
\ead{crisalod@gmail.com}
\credit{Investigation; Software; Writing - original draft}
\author[1,2]{V. Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Funding acquisition; Investigation; Supervision; Software; Writing - review \& editing}
\author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
\cormark[1]
\ead{mochan@fis.unam.mx}
\credit{Conceptualization; Funding acquisition; Investigation;
  Methodology; Supervision; Writing - review \& editing}
\address[1]{Centro de
  Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\address[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
  Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, México}
\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM.}
\cortext[cor1]{Corresponding author}
\begin{keywords}
  Porous Silicon\sep GRIN \sep Reflectance Spectra.\sep
\end{keywords}
\maketitle
\begin{abstract}
  A variety of optical devices and applications are based on
  layered systems which have a lateral gradient in both their
  refractive indices and their thickness. Simple fabrication of such
  systems can be carried out through the electrochemical synthesis of
  porous silicon (PS) using an etching current with a density $\bm
  j(\bm r_\|)$ that has a spatial variation along the surface of the
  sample. Thus, the possibility of predicting the local
  value of $\bm j(\bm r_\|)$ and the corresponding values of the porosity
  $p(\bm r_\|)$ and the etching rate $v(\bm r_\|)$ is desirable for a
  systematic design of these structures.
  In this work, we propose a simple analytical model based on a
  fast converging planewise summation of Coulomb potentials in two
  dimensional reciprocal space for the
  calculation of $\bm j(\bm r_\|)$ as a function of position
  within a prism shaped electrochemical cell. Some graded single layer PS samples
  were synthesized and their optical reflectance were used to
  estimate their local porosity $p(\bm r_\|)$ and thickness $d(\bm r_\|)$
  which, together with our model, were then used to obtain the basic
  calibration curves $p$ vs $\bm j$ and $v$ vs $\bm j$.
  The dependence of porosity and thickness with position was
  corroborated through scanning electron microscopy.
  Agreement was found between the calibration curves from
  different samples. Thus, from measurements on only one sample, our
  model allows us to obtain full calibration curves which may be
  used to predict, design, and fabricate more complex novel
  non-homogenous multilayered devices with lateral gradients for
  manifold applications.
\end{abstract}

>>>>

\begin{document}
\shorttitle{Model of the Current Density in the Electrochemical
  Synthesis of PS Structures with a Lateral Gradient}
\shortauthors{Ospina-Delacruz et al.}
\title[mode=title]{Analytical Model for the Current Density in
the Electrochemical Synthesis of Porous Silicon Structures with a
Lateral Gradient}
\author[1]{C. A. Ospina-Delacruz}[orcid=0000-0002-9609-3031]
\ead{crisalod@gmail.com}
\credit{Investigation; Software; Writing - original draft}
\author[1,2]{V. Agarwal}[orcid=0000-0003-2168-853X]
\fnmark[1]
\ead{vagarwal@uaem.mx}
\credit{Funding acquisition; Investigation; Supervision; Software; Writing - review \& editing}
\author[2]{W. L. Mochán}[type=editor,orcid=0000-0003-0418-5375]
\cormark[1]
\ead{mochan@fis.unam.mx}
\credit{Conceptualization; Funding acquisition; Investigation;
  Methodology; Supervision; Writing - review \& editing}
\address[1]{Centro de
  Investigación en Ingeniería y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\address[2]{Instituto de Ciencias F\'isicas, Universidad Nacional
  Autonóma de México, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, México}
\fntext[fn1]{On sabatical leave at ICF-UNAM from CIICAP-UAEM.}
\cortext[cor1]{Corresponding author}
\begin{keywords}
  Porous Silicon\sep GRIN \sep Reflectance Spectra.\sep
\end{keywords}
\maketitle
\begin{abstract}
  Layered optical devices with a lateral gradient
  can be fabricated through electrochemical synthesis of
  porous silicon (PS) using a position dependent etching current
  density  $\bm j(\bm r_\|)$. Predicting the local
  value of $\bm j(\bm r_\|)$ and the corresponding porosity
  $p(\bm r_\|)$ and etching rate $v(\bm r_\|)$ is desirable for their
  systematic design.
  We develop a simple analytical model for the
  calculation of $\bm j(\bm r_\|)$ within a prism shaped
  cell. Graded single layer PS samples
  were synthesized and their local calibration curves $p$ vs $\bm j$ and $v$
  vs $\bm j$ were obtained from our model and their reflectance spectra.
  The agreement found between the calibration curves from
  different samples shows that from one sample we
  could obtain full calibration curves which may be
  used to predict, design, and fabricate more complex
  non-homogenous multilayered devices with lateral gradients for
  manifold applications.
\end{abstract}
%  A variety of optical devices and applications are based on
%  layered systems which have a lateral gradient in both their
%  refractive indices and their thickness. Simple fabrication of such
%  systems can be carried out through the electrochemical synthesis of
%  porous silicon (PS) using an etching current with a density $\bm
%  j(\bm r_\|)$ that has a spatial variation along the surface of the
%  sample. Thus, the possibility of predicting the local
%  value of $\bm j(\bm r_\|)$ and the corresponding values of the porosity
%  $p(\bm r_\|)$ and the etching rate $v(\bm r_\|)$ is desirable for a
%  systematic design of these structures.
%  In this work, we propose a simple analytical model based on a
%  fast converging planewise summation of Coulomb potentials in two
%  dimensional reciprocal space for the
%  calculation of $\bm j(\bm r_\|)$ as a function of position
%  within a prism shaped electrochemical cell. Some graded single layer PS samples
%  were synthesized and their optical reflectance were used to
%  estimate their local porosity $p(\bm r_\|)$ and thickness $d(\bm r_\|)$
%  which, together with our model, were then used to obtain the basic
%  calibration curves $p$ vs $\bm j$ and $v$ vs $\bm j$.
%  The dependence of porosity and thickness with position was
%  corroborated through scanning electron microscopy.
%  Agreement was found between the calibration curves from
%  different samples. Thus, from measurements on only one sample, our
%  model allows us to obtain full calibration curves which may be
%  used to predict, design, and fabricate more complex novel
%  non-homogenous multilayered devices with lateral gradients for
%  manifold applications.
